NIRCam Faint and Bright Flux Calibration Plan

### 2017-04-11 ms.tex
I got rid of the figure with the NIRCam FOV and fibers since it's not redundant with another one. Also put in a comment that this is a draft in progress.
I added some updates to my replica of the AbsCal Plan report figure with the three clusters.

%\slugcomment{DHS White Paper}

@@

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration to accomplish its science goals.
One are where accurate flux calibration is especially important is dark energy science, which makes use of type Ia supernovae as standard candles.
Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe.
JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.\footnote{While NIRCam had internal lamps in original designs, the envelopes for the filaments broke during testing so the sources were removed.}

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.6\columnwidth]{nircam_wide_filters.png}
\includegraphics[width=.3\columnwidth]{calspec_and_new_clust.pdf}
\caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}. The three values are shown as upper, middle and lower limit error bars respectively. For comparison, three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red).
Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.
{\it Right:} The new expected G2 V calibrators as compared to the faintest G-type star in the calibration plan.}\label{fig:JWStcalsWideF}
\end{figure}

@@

\section{NIRCam Footprint}
\begin{figure}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{nircam_fov_fibers.pdf}
\caption{NGC 2420 fibers on the first pass with the FOV of both the A and B modules of NIRCam.
Only 10 stars fit within NIRCam's FOV.}\label{fig:NCFOV}
\end{figure}

>>>>

\slugcomment{\textcolor{red}{NOTE, this is a work in progress}}

@@

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration to accomplish its science goals.
One area where accurate flux calibration is especially important is dark energy science, which makes use of type Ia supernovae as standard candles.
Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe.
JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.\footnote{While NIRCam had internal lamps in original designs, the envelopes for the filaments broke during testing so the sources were removed.}

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.48\columnwidth]{nircam_wide_filters.png}
\includegraphics[width=.48\columnwidth]{calspec_and_new_clust.pdf}
\caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}. The three values are shown as upper, middle and lower limit error bars respectively. For comparison, three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red).
Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.
{\it Right:} The new expected G2 V calibrators as compared to the faintest G-type star in the calibration plan.}\label{fig:JWStcalsWideF}
\end{figure}

@@
